### 2017-02-01 local-capability-machine.tex
Added proof of value predicate mono wrt private future for global caps.

\begin{lemma}[$\mathit{writeCondition}$ global monotonicity w.r.t $\futurestr$]
  \label{lem:writecond-mono-priv}
  If
  \begin{itemize}
  \item $W' \futurestr W$
  \item $\iota \in \{\iota^\nwl,\iota^{(\nwl,p)}\}$
  \item $\npair{(\start,\addrend)} \in \writeCond{}(\iota,\glob)(W)$
  \end{itemize}
  then
  \[
    \npair{(\start,\addrend)}\in \writeCond{}(\iota,\glob)(W')
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:writecond-mono-priv}]
  % TODO
\end{proof}

\begin{lemma}[$\mathit{writeCondition}$ downwards-closed]
  \label{lem:writecond-dc}
  If 
  \begin{itemize}
  \item $n' \leq n$
  \item $\iota \in \{\iota^\pwl,\iota^\nwl,\iota^{(\nwl,p)}\}$
  \item $\npair{(\start,\addrend)} \in \writeCond{}(\iota,\gl)(W)$
  \end{itemize}
  then 
  \[
    \npair[n']{(\start,\addrend)} \in \writeCond{}(\iota,\gl)(W)
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:writecond-dc}]
  $\writeCond{}(\iota,\glob)(W)$ picks a $\perma$ region from $W$. $\perma$ regions are persistent over $\futurestr$, so we can use the region that the assumption gives us.
\end{proof}

@@

\subsubsection{Value relation}
\begin{lemma}[Global capabilities monotone wrt $\futurestr$]
  \label{lem:stdvr-glob-priv-mono}
  \begin{align*}
    & \forall n, \perm, \start, \addrend, \addr, W, W' \ldotp \\
    & \quad  \npair{\stdcap[(\perm,\glob)]} \in \stdvr(W) \land W' \futurestr W\\
    & \qquad \Rightarrow \npair{\stdcap[(\perm,\glob)]} \in \stdvr(W') 
  \end{align*}
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:stdvr-glob-priv-mono}]
  Assume 
  \begin{enumproof}
  \item $W' \futurestr W$
  \item $\npair{\stdcap[(\perm,\glob)]} \in \stdvr(W)$
  \end{enumproof}
  and show
  \[
    \npair{\stdcap[(\perm,\glob)]} \in \stdvr(W')
  \]
  to this end consider all the possible cases of $\perm$:
  \begin{enumproof}
    \item $\perm = \noperm$\\
      Trivial
    \item $\perm = \readonly$ \\

    \item $\perm = \readwrite$ \\

    \item $\perm = \rwl$ \\

    \item $\perm = \exec$ \\

    \item $\perm = \rwx$ \\

    \item $\perm = \rwlx$ \\
  \end{enumproof}

>>>>

\begin{lemma}[$\mathit{writeCondition}$ global monotonicity w.r.t $\futurestr$]
  \label{lem:writecond-mono-priv}
  If
  \begin{itemize}
  \item $W' \futurestr W$
  \item $\iota \in \{\iota^\nwl,\iota^{(\nwl,p)}\}$
  \item $\npair{(\start,\addrend)} \in \writeCond{}(\iota,\glob)(W)$
  \end{itemize}
  then
  \[
    \npair{(\start,\addrend)}\in \writeCond{}(\iota,\glob)(W')
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:writecond-mono-priv}]
  $\writeCond{}(\iota,\glob)(W)$ picks a $\perma$ region from $W$. $\perma$ regions are persistent over $\futurestr$, so we can use the region that the assumption gives us.
\end{proof}

\begin{lemma}[$\mathit{writeCondition}$ downwards-closed]
  \label{lem:writecond-dc}
  If 
  \begin{itemize}
  \item $n' \leq n$
  \item $\iota \in \{\iota^\pwl,\iota^\nwl,\iota^{(\nwl,p)}\}$
  \item $\npair{(\start,\addrend)} \in \writeCond{}(\iota,\gl)(W)$
  \end{itemize}
  then 
  \[
    \npair[n']{(\start,\addrend)} \in \writeCond{}(\iota,\gl)(W)
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:writecond-dc}]
  % TODO
\end{proof}

@@

\subsubsection{Value relation}
\begin{lemma}[Global capabilities monotone wrt $\futurestr$]
  \label{lem:stdvr-glob-priv-mono}
  \begin{align*}
    & \forall n, \perm, \start, \addrend, \addr, W, W' \ldotp \\
    & \quad  \npair{\stdcap[(\perm,\glob)]} \in \stdvr(W) \land W' \futurestr W\\
    & \qquad \Rightarrow \npair{\stdcap[(\perm,\glob)]} \in \stdvr(W') 
  \end{align*}
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:stdvr-glob-priv-mono}]
  Assume 
  \begin{enumproof}
  \item $\perm \not\in \{\rwl, \rwlx\}$
  \item $W' \futurestr W$
  \item $\npair{\stdcap[(\perm,\glob)]} \in \stdvr(W)$
  \end{enumproof}
  and show
  \[
    \npair{\stdcap[(\perm,\glob)]} \in \stdvr(W')
  \]
  to this end consider the possible cases of $\perm$ and show that each of the necesary conditions hold:
  \begin{enumproof}
    \item $\perm = \noperm$\\
      Trivial
    \item $\perm = \readonly$ \\
      Follows from Lemma~\ref{lem:readcond-mono-priv}.
    \item $\perm = \readwrite$ \\
      Follows from Lemma~\ref{lem:readcond-mono-priv} and Lemma~\ref{lem:writecond-mono-priv}.
    \item $\perm = \exec$ \\
      Follows from Lemma~\ref{lem:readcond-mono-priv} and Lemma~\ref{lem:execcond-mono-priv}.
    \item $\perm = \rwx$ \\
      Follows from Lemma~\ref{lem:readcond-mono-priv}, Lemma~\ref{lem:writecond-mono-priv}, and Lemma~\ref{lem:execcond-mono-priv}.
    \item $\perm = \entry$ \\
      Lemma~\ref{lem:entrycond-mono-priv}
  \end{enumproof}
\end{proof}
